Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-08-13 article.tex
Update article.tex

The iterative nature, or the ability to show the difference in probable outcomes of different sets of events and their uncertainty allows for the ability to conduct inference. This type of Bayesian inference shows the difference between the likelihood of various outcomes with and without different evidence of prior nodes outcomes being present. The sets of different outcomes then stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods.

One of the greatest abilities within this style of inference is Marginalization. In which, the outcome of a particular event can be determined irrespective of other outcomes. This type of marginalisation is intuitively represented as nodes conditional independence is illustrated inherently through the structure of the graph by its edges.

Bayesian Networks created in this study were created using BayesFusion \citep{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities. The use of Bayes fuse software was used both through the GUI interface and the SMILE API \citep{bayesfusionGeNIeModelerUSER2022} system using C++ \citep{ISO:2012:III}.

\subsection{Elicitation}

The Bayesian Network was constructed using a mixture of data and expert elicitation. The format followed recommendations from \cite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}. Where, we progressed iteratively through from problem definition, to structure, to parametarisation, and then to validation. Experts were initially informed regarding the process to establish an understanding of what each step would be comprised of, as well as highlighting common pitfalls and how we would address them. With common problems being listed by both authors being:
\begin{enumerate}
        \item Not understanding the problem context
        \item complexity without value
        \item Getting arc directions wrong
        \item too many parent nodes
        \item Bias expert estimates
        \item Inconsistent probabilities
        \item Being absolutely certain
\end{enumerate}
To address these issues, experts were kept well-informed of them, as well as variable definitions and problem scope. Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency. Communication included in-person and electronic one-on-ones and group sessions; with elicitation of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.

@@

\subsection{CPT interpolating}

As is often the case, the most arduous endeavour is to attribute probabilities to events defined within the Bayesian Network \citep{korbBayesianArtificialIntelligence2011}. Due to the growing complexity of the network throughout the study each event was described by binary classes. With the classes depicting a positive or negative contribution to a vineyard's environmental outcome. Furthermore, the complexity of the variables, particularly water use, were overwhelmingly interrelated to operations across the vineyard. To attempt to capture this complexity but not dilute the ability to work with various scenarios the conditional probabilities were interpolated.

This method utilised interpolation between two anchored points. One point represented the case of all factors being true/positive and the other represented all factors being false/negative. The interpolation was achieved by designating each factor an attributed weight; where, weights were indicative of a factor's overall influence to its child node. During workshop discussion participants were the most comfortable using scores out of 10 to describe a factor's influence on its child node.

Using this method, any given probability can be calculated using
\begin{equation}
        p=x\sum_{i}^{n} + y\sum_{m}^{i} 
\end{equation},
for n number of true or contributing factors and m false or not contributing factors. We know the solutions for when all contributing factors are true ($p_t$) or all were false ($p_f$). Where,
\begin{equation}
        p_t=x\sum_{i}^{n} 
        \text{ and }
        p_f=y\sum_{m}^{i}
\end{equation}.
From here values for $x$ and $y$ are able to be derived using the sum of the provided weights.

\subsection{Validation}

The method for validation sought to address concerns presented by \citep{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity. Validation steps were partly incorporated during the process of constructing the Bayesian network itself. Specifically when considering the nomological validity of the network; the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario. In part, the selection process for experts, aspired to be diverse within their regional knowledge and expertise in an attempt to broaden the ability to critique choices. Although it was agreed that multiple scenarios were well captured by the trees structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions. This requirement aligned with literature, which highlighted how regional variation is considered a driving factor for many vineyard outcomes and priorities \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.

The Face and content validity of the network was questioned directly by the expert panel through the structure and conditional probability phases. The choice of binary discretisation was due to two reasons; that it captured the relevant contribution to the node in question and limited the model from becoming to overly complex and circumstantial. This helped to avoid some overtly specific scenarios in favour for broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations. This approach went hand in hand with the content validation. Where, it was found that the limitation of the model was primarily regional, which aligned again with the findings of other researchers \citep{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}. Specifically, the question of water resources, which was central to the model and highly interrelated \citep{carmonaUseParticipatoryObjectOriented2011}.

Similarly, the convergent validity of the model was accomplished through the broader discretisation of nodes into the binary forms of positive and negative affects on the environmental impact of the vineyard. This manner of discretisation allowed a clear delineation in localised subnetworks within the model. The alignment of the model to other research helped to further answer questions of concurrent validation. In that, it was found that other studies emphasised the same variables selected by our experts. This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes \cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}. Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}.

@@

The structure of the model itself was similar to other models in the presence of variables but differed in some of their relation due to the terminal node being environmental impact. The paramitisation of the nodes did differ to other studies, as every node was related and thought of with regard, to the terminal node and how they subsequently affected the environmental outcomes of a vineyard and not other more prevalent outcomes such as yield \citep{laurentReviewIssuesMethods2021}. The discriminant validity of the model was highlighted through the acknowledgement of the model's requirement to be tuned to any specific wine region before being able to be properly employed. Furthermore, the predictive validity was able to be well established through two methods, the use of a case study and the consideration of extreme outcomes.

\subsection{Sensitivity analysis}

The sensitivity analysis conducted in this study utilised the Bayesian Network software GeNie, implementing the algorithm developed by \cite{article}; an optimisation of \autocite{Castillo1996ANM} and \cite{Gaag1998PracticableSA}. The method allows for efficient computation of the influence of parameter variations on the output probabilities of a Bayesian network, making it particularly suitable for complex models. Sensitivity was calculated on the terminal node 'Environmental Impact' to reflect its sensitivity to changes in other nodes.

The process utilises two outward and an inward propagation across a junction tree, a data structure representing the Bayesian network. These propagations are essential for establishing the necessary cliques that allow for the calculation of the sensitivity function using the coefficients $\gamma$ and $\delta$.

@@

Where $y$ is the posterior marginal of interest, given evidence $e$, with respect to the parameter $x$.

@@

Due to the regional limitations of the model, experts proposed a case study of a specific and well understood region: Coonawarra in South Australia. The choice of the region was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to winegrowing. The Coonawarra BN was built off of the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel. Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for undervine operations and more purposeful undervine management, as well as the inclusion of further soil based factors that could be significant for particular sites.

@@

The key factors identified were defined as shown in Table \ref{tab:definitions}. By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed by the industry panel. The quantification of each factor allowed for a systematic assessment of their impacts. For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact. Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).

% How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
% Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
% Results: Use the agreed upon definitions to fully realise factors and their impact.
% 
% Please add the following required packages to your document preamble:
% \usepackage{booktabs} TODO: check the BN definitions align properly.
% 

@@

    \textbf{Variable name} & Definition & \textbf{Ideal Class} & Not Ideal Class \\ \midrule

@@

\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}

The relationships between the concepts defined by the industry panel are depicted in~\ref{figure:generalBN} as nodes in the Bayesian Network. The network highlights which factors are influenced by others in the form of an acyclic directed graph. Notably, the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water. It also illustrates the complex nature of variables such as water and their interrelatedness.

@@

    % What are the relationships between these factors in the Australian winegrowing industry?
    %     Purpose: Explore and understand the causal and correlated relationships among the factors.
    %     Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
% 
\begin{figure}[h!]
    \centering
    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
    \caption{The resultant Bayesian network after initial discussions of how factors that contribute to environmental impact are related. Illustrating the general relationships that exist between vineyard factors and environmental impact in Australian winegrowing.}\label{fig:generalBN}
\end{figure}

The BN provided a comprehensive overview of how factors defined by the industry panel, would interact. Showing not only direct relationships but also how changes in one factor can propagate through the network to affect others. This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry. This network illustrates the complexity of interactions that define environmental sustainability in Australian winegrowing. Furthermore, the extent of relationships helps to intrinsically show the importance of variables such as water; which is prolific in how it is interconnected with other vineyard aspects.

Figure~\ref{fig:generalBN}, illustrates the importance of water, disease/pests and climate through their prominent connections and numerous child nodes. Variables such as fuel use and soil management are resultant children nodes that connect these external pressures to decisions that offer potential solutions or interventions to aid in pursuing more sustainable outcomes.

@@

The bibliometric analysis using Leximancer, revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry. The most prominent concept was water (see Table \ref{tab:lexi}). The critical importance of other variables being measured by their comparative appearance in articles relative to water (making water 100\%).

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]\label{tab:lexi}
    \begin{tabular}{@{}lrr@{}}
    \toprule
    \textbf{Concept} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
    water & 1321 & 100 \\
    change & 817 & 62 \\
    climate & 789 & 60 \\
    disease & 646 & 49 \\
    change & 569 & 43 \\
    grapevine & 565 & 43 \\
    viticulture & 565 & 43 \\
    soil & 450 & 34 \\
    plant & 425 & 32 \\
    different & 300 & 23 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

The most significant concepts along with "water", included "change", "climate", and "disease". These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see \ref{tab:lexi}). Furthermore, change and climate were kept separate to illustrate the variety of different changes, such as in practice, legislation and resource abundance. Additionally, although not in the top 10; "soil", "region", "practices", and "legislation" also appear to be dominant features within the literature. These factors are critical as they shape the environmental strategies employed by vineyards.

The prominence of different factors is visually described in Figure \ref{fig:lexi}, with the network depicting the frequency of these concepts appearing together. With the major concepts of these features being change, grapevine, water and land. These concepts illustrated the overarching theme between how the different concepts are connected, which showed very similar themes to that of the industry panel.

@@

A key difference between the concepts from Leximancer and the Bayesian Network was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease. With these concepts being related to the operations in fields as a result of changing practices or implementing different pest controls. Together these outputs provide a comprehensive overview of the key factors affecting environmental sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement. This analysis underscores the multifaceted nature of sustainability, highlighting both the primary concerns and the interconnected secondary factors that must be managed on the ground.

\subsection{Sustainability specifics: Coonawarra Winegrowing}

Located in South Australia's Limestone Coast zone, Coonawarra is characterised by its cooler Australian climate and the unique geology of the limestone coast, which provides an excellent foundation for viticulture. The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}. Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around environmental sustainability practices to specific regional factors.

>>>>

The ability to present different probable outcomes for various sets of events and their associated uncertainties enables the conduction of inference. This inference shows the difference between the likelihood of various outcomes with and without different evidence of prior nodes outcomes being present. The sets of different outcomes then stored as a joint probability distribution, which can be decomposed into the conditional probabilities of each set of possible events occurring and their likelihoods. One of the greatest abilities of this type of inference is Marginalization. In which, the outcome of a particular event can be determined irrespective of other outcomes. This type of marginalisation is intuitively represented as nodes conditional independence and illustrated inherently through the structure of the graph by its edges.

Bayesian Networks created in this study were created using BayesFusion \citep{bayesfusionGeNIeModelerUSER2022} to calculate the networks and their probabilities. The Bayes fuse software was used both through the GUI interface and the SMILE API \citep{bayesfusionGeNIeModelerUSER2022} system using C++ \citep{ISO:2012:III}.

\subsection{BN Construction and Quantification}

The Bayesian Network was constructed using a mixture of data and expert elicitation, following the format recommended by \textcite{korbBayesianArtificialIntelligence2011,pitchforthProposedValidationFramework2013}. The process progressed iteratively through problem definition, structure, parameterization, and validation. Initially, experts were informed about the process to ensure a clear understanding of each step and to highlight common pitfalls, as well as how these would be addressed. Some of the common problems identified by both authors include a lack of understanding of the problem context, the introduction of complexity without value, incorrect arc directions, an excessive number of parent nodes, biased expert estimates, inconsistent probabilities, and an unwarranted certainty in estimates. To address these issues, experts were kept well-informed of them, as well as variable definitions and problem scope. Open communication was maintained during the entire process to help answer questions regarding the model, process, and to maintain transparency. Communication included in-person and electronic one-on-ones and group sessions; with elicitation of expert knowledge being primarily conducted through a series of workshops with the panel of industry experts.

@@

\subsection{CPT interpolation}

As is often the case, the most arduous endeavour was attributing probabilities to events defined within the Bayesian Network \citep{korbBayesianArtificialIntelligence2011}. For reasons of comparability between nodes, disparate and often sparse data or expert judgement, and due to the complexity of the network, each event was described by binary classes. The classes represented a positive or negative contribution to a vineyard's environmental outcome helping to reduce this complexity. Furthermore, the intricacy of variables, particularly water use, were overwhelmingly interrelated to operations across the vineyard. To attempt to capture this complexity but not dilute the ability to work with various scenarios experts were asked to provide key input into complex CPT cells and the CPT cells were interpolated. The experts then reviewed and amended or approved the derived CPTs.

This interpolation method utilised filling in cells between two anchored points. One point represented the case of all factors being true/positive and the other represented all factors being false/negative. The interpolation was achieved by designating each factor an attributed weight, where weights were indicative of a factor's overall influence to its child node. During workshop discussion participants were the most comfortable using scores out of 10 to describe a factor's influence on its child node.

Using this method, a given probability was calculated using
\begin{equation}
        p=x\sum_{i}^{n}\alpha_{i} + y\sum_{i}^{m}\beta_{i} 
\end{equation},
n count of true (or ideal states) and m false (or not ideal states) factors. The solutions for when all contributing factors are true ($p_t$) or all are false ($p_f$) is,
\begin{equation}
        p_t=x\sum_{i}^{n}\alpha_{i} 
        \text{ and }
        p_f=y\sum_{i}^{m}\beta_{i}
\end{equation}.
The values for $x$ and $y$ can be derived using the sum of the provided BN weights. An assumption of 'smoothness' is taken between worst and best case scenarios when utilising this method. All possible combinations between all states being true (or ideal) and all being false (not ideal) are also mirrored such, with the only consideration being given, is that of how heavily weighted a variables state is compared to the others.

\subsection{BN Validation}

The method for validation sought to address criteria presented by \textcite{pitchforthProposedValidationFramework2013}; who listed the following:  nomological, face, content, concurrent, convergent, discriminant and predictive validity. Nomological validity refers to ensuring that the BN fits within a broader theoretical context, aligning with established literature. Face validity involves evaluating whether the model appears to be a valid representation based on expert judgment. Content validity checks that the model includes all relevant factors and relationships from both literature and expert knowledge, ensuring nothing critical is omitted. Concurrent validity is concerned with whether the BN or its components behave consistently when compared with other similar networks. Convergent validity assesses how closely the BN aligns with models that describe similar systems, while discriminant validity ensures that the BN is distinct from models representing different systems. Finally, predictive validity examines the BN's ability to accurately predict system behavior.Validation steps were partly incorporated during the process of constructing the Bayesian network itself. When considering the nomological validity of the network, the expert panel was asked directly regarding its ability to extrapolate beyond a single region, or scenario. The selection process for experts, encouraged diversity in their regional knowledge and expertise in order to broaden the ability to critique choices. Although it was agreed that multiple scenarios were well captured by the BNs structure, minor additions would be needed to encapsulate the differences between specific winegrowing regions \citep{abbalDecisionSupportSystem2016,agostaRegionalClimateVariability2012,soarClimateDriversRed2008}.

The face and content validity of the network was questioned directly by the expert panel through the structure and conditional probability phases. This helped to avoid some overtly specific scenarios in favour of broader vineyard decisions, whilst allowing the model to address these behaviours in the future by specifically targeting a region and incorporating its considerations. This approach went hand in hand with the content validation, where, it was found additional nodes needed to be added to the general model ro reflect important regional factors \citep{abbalDecisionSupportSystem2016,ellisUsingBayesianGrowth2020,agostaRegionalClimateVariability2012,barriguinhaVineyardYieldEstimation2021,brockRelationSoilOrganic2011}. 
% Specifically, the question of water resources, which was central to the model and highly interrelated \citep{carmonaUseParticipatoryObjectOriented2011}.

Similarly, the convergent validity of the model was accomplished through the checking the alignment of the model to other research, which helped to further answer questions of concurrent validation. This process was undertaken after the regional models were developed in unison with the literature review and creation of leximancer concept map. It was found that other studies emphasised the same variables selected by our experts. This was especially true regarding the consideration of yield and regional factors that influence vineyard outcomes \cite{abbalDecisionSupportSystem2016,campsGrapeHarvestYield2012,hallWithinseasonTemporalVariation2011}. Furthermore, these types of variables are highly prevalent in greater agriculture studies that emphasise general outcomes and resource use such as yield and water respectively \citep{heFruitYieldPrediction2022,laurentLocalInfluenceClimate2022}.

@@

The factors within the BN had similar parent nodes to factors that appeared in other models from the literature (i.e yield generally utilised area, water, fuel as predictors), although there were key differences. The differences were primarily due to the consideration of nodes as factors that related and were thus thought of with regard, to environmental impact which changed how nodes subsequently affected the environmental outcomes of a vineyard and not other more common focus outcomes from the literature such as water use or yield; which were often observed in isolation \citep{laurentReviewIssuesMethods2021}. The discriminant validity of the model was highlighted through the acknowledgement of the model's requirement to be tuned to any specific wine region before being able to be properly employed. Furthermore, the predictive validity was able to be well established through two methods, the use of a case study and the consideration of extreme outcomes.

\subsection{Sensitivity analysis}
% TODO: add a paragraph about what you mean by sensitivity analysis and why a BN facilitates this, its important! KM
The sensitivity analysis conducted in this study utilised the Bayesian Network software GeNie, implementing the algorithm developed by \textcite{article}; an optimisation of \textcite{Castillo1996ANM} and \textcite{Gaag1998PracticableSA}. The method allowed for efficient computation of the influence of parameter variations on the output probabilities of the BNs terminal node 'Environmental Impact'.

The process utilises two outward and one inward propagation across a junction tree, a data structure that represents the Bayesian network by organizing its nodes into a tree of cliques, where each clique is a subset of nodes that are fully connected within the network. Propagation refers to the method of passing messages (or updating beliefs) through this junction tree to ensure consistency across the network, allowing for the efficient calculation of probabilities. These propagations are essential for establishing the necessary cliques that allow for the calculation of the sensitivity function using the coefficients $\gamma$ and $\delta$.

@@

where $\alpha$, $\beta$, $\gamma$ and $\delta$ are constants with respect to $x$. $y$ is the posterior marginal of interest, which refers to the probability distribution of a subset of variables (in this case, $y$) after taking into account the given evidence $e$, with respect to the parameter $x$ (a factor or state of a node within the BN).

@@

% #TODO: make sure this fits in ~ moved paragraph
Located in South Australia's Limestone Coast zone, Coonawarra is characterised by its cooler Australian climate and the unique geology of the limestone coast, which provides an excellent foundation for viticulture. The Coonawarra winegrowing region is renowned for its exceptional wine quality, particularly its Cabernet Sauvignon \cite{hallidayAustralianWineEncyclopedia2009}. Due to the region's distinct characteristics and the expert panels' expertise, this region was the ideal case study for applying Bayesian Networks using the expert panels overarching ideas around environmental sustainability practices to specific regional factors.

As discussed above the expert advisory panel proposed the development of a reigonal model to augment and focus the primary general model. For specificity the panel proposed a case study of a specific and well understood region: Coonawarra in South Australia. The choice of the region was due to the prevalence of data within and around the region, as well as experts' understanding of the region's unique challenges and benefits to winegrowing. The Coonawarra BN was based on the original Bayesian Network's structure with site specific conditional probabilities being entered and scrutinised by the expert panel. Difference in factor interactions were further discussed by the panel, resulting in two distinct BN models that influenced two types of approaches; primarily differing between opportunity based tractor use for undervine operations and more purposeful undervine management, as well as the inclusion of further soil based factors that could be significant for particular sites.

@@

The key factors identified by the industry panel and their agreed definitions are shown in Table \ref{tab:definitions}. By utilising these definitions, each factor's contribution to environmental sustainability were quantified and assessed by the industry panel. The quantification of each factor allowed for a systematic assessment of their impacts. For example, "Water Use" was quantified as "High" or "Low," enabling a straightforward assessment of its environmental impact. Similarly, other factors were defined and quantified to ensure their contributions to sustainability were measurable; with each being of the two general categories ideal and not ideal (low and high respectively for water use).

% How can these key factors be rigorously defined so that they are quantifiable contributions to environmental sustainability?
% Purpose: Develop the factors into well-defined and measurable impacts on environmental sustainability.
% Results: Use the agreed upon definitions to fully realise factors and their impact.
% 
% Please add the following required packages to your document preamble:
% \usepackage{booktabs} TODO: check the BN definitions align properly.
%

% TODO: table caption!@!

@@

    \textbf{Factor name} & Definition & \textbf{Ideal Class} & Not Ideal Class \\ \midrule

@@

% TODO: you need a new heading as its the BN strucutre not key factors
\subsection{Key Factors Impacting Environmental Sustainability in Australian Winegrowing}

The relationships between the facets in Table \ref{tab:definitions}  as agreed by the industry panel, are depicted in the BN model in Fig ~\ref{figure:generalBN}. The BN highlights which factors are influenced by others in the form of an acyclic directed graph. Notably, the key factors influencing environmental impact centre around the application of agrochemical sprays, soil management, pest/disease and water. It also illustrates the complex nature of variables such as water and their interrelatedness.

@@

    % What are the relationships between these factors in the Australian winegrowing industry?
    %     Purpose: Explore and understand the causal and correlated relationships among the factors.
    %     Results: Use the generic BN to illustrate the overall agreed upon relationships between discussed factors.
% 
\begin{figure}[h!]
    \centering
    % \includegraphics[width=\textwidth]{path_to_coonawarra_bn_figure} % Adjust the width as needed
    \caption{The resultant BN illustrating the relationships between vineyard factors and environmental impact in Australian winegrowing.}\label{fig:generalBN}
\end{figure}
% TODO: expand the description of the figure to indflude the blue, green ghold and pink definitions.

% The BN provided a comprehensive overview of how factors defined by the industry panel, would interact. Showing not only direct relationships but also how changes in one factor can propagate through the network to affect others. This understanding is crucial for developing targeted interventions and policies aimed at improving sustainability in the winegrowing industry. This network illustrates the complexity of interactions that define environmental sustainability in Australian winegrowing. Furthermore, the extent of relationships helps to intrinsically show the importance of variables such as water; which is prolific in how it is interconnected with other vineyard aspects.

% TODO: expand, you have built the reader up to this point so do justice to the BN!
Figure~\ref{fig:generalBN}, illustrates the importance of water, disease/pests and climate through their prominent connections and numerous child nodes. Variables such as fuel use and soil management are resultant children nodes that connect these external pressures to decisions that offer potential solutions or interventions to aid in pursuing more sustainable outcomes.

@@

% TODO: Reults of lit review: no. articles, etc Here

The bibliometric analysis using Leximancer revealed key concepts and their relevance to environmental sustainability in the Australian winegrowing industry. The most prominent concept was water (see Table \ref{tab:lexi}). The critical importance of other variables is indicated by their comparative appearance in articles relative to water (making water 100\%).

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]\label{tab:lexi}
    \caption{Table \ref{tab:lexi} Table \ref{tab}: Key Concepts Identified in the Bibliometric Analysis of Environmental Sustainability in the Australian Winegrowing Industry.}
    \begin{tabular}{@{}lrr@{}}
    \toprule
    \textbf{Concept} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
    water & 1321 & 100 \\
    change & 817 & 62 \\
    climate & 789 & 60 \\
    disease & 646 & 49 \\
    change & 569 & 43 \\
    grapevine & 565 & 43 \\
    viticulture & 565 & 43 \\
    soil & 450 & 34 \\
    plant & 425 & 32 \\
    different & 300 & 23 \\ \bottomrule
    \end{tabular}
    \end{table}

@@

The most significant concepts along with water, included change, climate, and disease. These terms highlight the focus on adapting to climate change and managing plant diseases, both of which are crucial for maintaining sustainable practices (see Table \ref{tab:lexi}). Furthermore, change and climate were kept separate to illustrate the variety of different changes, such as in practice, legislation and resource abundance. Additionally, although not in the top 10; "soil", "region", "practices", and "legislation" also appear to be dominant features within the literature. These factors are critical as they shape the environmental strategies employed by vineyards.

The prominence of different factors is visually described in Figure \ref{fig:lexi}, with the size of nodes in the diagram depicting the frequency of these concepts appearing in literature. Figure \ref{fig:lexi} also illustrates the connection between concepts through edges, and overlaying the most related concepts, change, grapevine, water and land as coloured areas on the diagram. With the most related concepts being of similar themes to that of the industry panel's Bayesian Network.

@@

A key difference between the concepts from the literature search and the BN based on the industry panel was the rarity in how secondary and tertiary drivers of industry such as fuel or electricity use, were connected to primary sustainable concerns such as disease (even though disease was quite prominent in both). 
% With these concepts being related to the operations in fields as a result of changing practices or implementing different pest controls. Together these outputs provide a comprehensive overview of the key factors affecting environmental sustainability in the Australian winegrowing industry, offering valuable insights into areas of focus and potential improvement. This analysis underscores the multifaceted nature of sustainability, highlighting both the primary concerns and the interconnected secondary factors that must be managed on the ground.

\subsection{Region-specific BN: Coonawarra}
